### 2024-01-20 Dissertation/userstyles.tex
dissertation_v2: Dissertation/userstyles.tex

\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\fontsize{10pt}{12pt}\selectfont\ttfamily,
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,
	breaklines=true,
	captionpos=b,
	commentstyle=\color{gray},
	keepspaces=true,
	keywordstyle=\color{violet},
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{gray},
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	stringstyle=\color{green},
	tabsize=2,
	xleftmargin={\lmarg}
}

>>>>

\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\fontsize{10pt}{12pt}\selectfont\ttfamily,
	breakatwhitespace=false,
	breaklines=true,
	captionpos=b,
	commentstyle=\color{gray},
	keepspaces=true,
	keywordstyle=\color{violet},
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{gray},
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	stringstyle=\color{green},
	tabsize=2,
	xleftmargin={\lmarg}
}
